---
description: How to update graphs stored in Chart Studio with ggplot2.
display_as: chart_studio
language: ggplot2
layout: base
name: Updating Graphs Stored In Chart Studio
order: 10
output:
  html_document:
    keep_md: true
permalink: ggplot2/file-options/
thumbnail: thumbnail/horizontal-bar.jpg
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```
### Save ggplot2 Plot To Chart Studio

Using the `plotly` ggplot2 package, you can create a Chart Studio figure based on your ggplot2 chart. Simply pass your chart as a parameter to the `api_create()` function:

```{r}
library(plotly)

p <- qplot(mpg, wt, data = mtcars, size = cyl)

api_create(p)
```

### How To Overwrite An Existing Plot

By default, when you call `api_create()`, a new plot is created in your Chart Studio account with its own unique URL.

If you would like to overwrite an existing plot in your Chart Studio account and keep the same URL, then supply a `filename` as an extra parameter to the `api_create()` function. This will keep the same URL for the plot. 

```{r}
library(plotly)

p <- qplot(mpg, wt, data = mtcars, size = cyl)

api_create(p, filename = "name-of-my-plotly-file")
```

### Saving Plots In Folders

If the `filename` parameter contains the character "/", then the `api_create()` function will save that plot in a folder in your Chart Studio account. 

This option is only available for [Chart Studio Enterprise subscribers](https://plotly.com/online-chart-maker/)

```{r}
library(plotly)

p <- qplot(mpg, wt, data = mtcars, size = cyl)

api_create(p, filename="r-docs/name-of-my-chart-studio-file")
```

### Viewing Saved Plots

View the ggplot2 graphs you have saved in your Chart Studio account at [https://plotly.com/organize](https://plotly.com/organize).